An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-30 EconGrowth.Rnw
Updated references.

\item{Reese: Review EIA IES database for any revisions to historical data.}
\item{Reese: Add food energy intake for all countries from FAO.}
\item{Reese: Fix the energy sankey diagram from the seminar.}
\item{Heun: Include the adjusted sankey diagram in the seminar.}
\item{Heun: Eliminate non-developed countries from 9-panel partial residual plots.}
\item{Heun: Obtain answers to questions I put to Caleb.}
\item{Heun: Add references from Lucas.}

@@

@@

Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet{BLS:2013a}. Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.

@@

Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association. Support for Matthew Kuperus Heun was provided by a Calvin College Research Followship. Funding for Martin de Wit was provided by *******. The authors thank Loren L. Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.

>>>>

\item{Reese: Review EIA IES database for any revisions to historical data}
\item{Reese: Add food energy intake for all countries from FAO}
\item{Reese: Fix the energy sankey diagram from the seminar}
\item{Heun: Include the adjusted sankey diagram in the seminar}
\item{Heun: Eliminate non-developed countries from 9-panel partial residual plots}
\item{Heun: Add references from Lucas}

@@

\item{\st{Heun: Obtain answers to questions I put to Caleb about the energy section}}
\item{\st{Heun: Add Warr to acknowledgements}}
\item{\st{Heun: Include EIA graphic (instead of IEA graphic) in the seminar}}

@@

Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.

@@

Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association. Support for Matthew Kuperus Heun was provided by a Calvin College Research Followship. Funding for Martin de Wit was provided by *******. The authors thank Loren L. Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein. The authors are grateful to Benjamin S. Warr (INSEAD) for providing the REXS database \citep{Warr:2012a}.
